Friends Get More Money, Attention, and Handshakes: Xinhua, Diplomacy, and Chinese Foreign Aid

### 2022-07-14 05_Presentation/aiddata_presentation.Rmd
added china data 2.0

-   Like Western donors, China should wield international aid, in part, to generate goodwill toward Beijing.

<!-- -->

-   We know that this has been important for the US (e.g. tsunami relief to Indonesia in 2004)

-   There is some evidence that the perception fo Beijing's influence in developing countries is growing (per differences in 2014 and 2017 waves of AidData surveys of policymakers in 126 countries)

@@

The obscurity may have more to do with capacity than intention (Dreher et al. 2018).

But transparency remains.

@@

-   AidData's *China's Public Diplomacy Dashboard*

-   Cline Center for Advanced Social Research's *Global News Index and Extracted Features Repository*

@@

-   AidData's *Global Chinese Development Finance Dataset*

@@

-   Diplomatic visits usually come with policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.

@@

H1: When developing countries receive more media exposure in *Xinhua*, they receive more foreign aid from China.

H2: When developing countries host more Chinese high-level diplomatic visits, they receive more foreign aid from China.

@@

| Variable               | Description                                                                                        | Source                                                                                               |
|------------------------|----------------------------------------------------------------------------------------------------|------------------------------------------------------------------------------------------------------|
| Outcome                | bilateral ODA-like flows from China to developing countries                                        | AidData's *Chinese Development Finance Dataset*                                                      |
| Explanatory Variable 1 | the number of bilateral diplomatic visits hosted by recipients from Beijing                        | AidData's compiled yearly counts of bilateral official diplomatic visits from China                  |
| Explanatory Variable 2 | the number of times a developing country is mentioned in a year in the English edition of *Xinhua* | compiled from millions of *Xinhua* articles scraped by the Cline Center for Advanced Social Research |

@@

Miles D. Williams: milesdw2\@illinois.edu

Lucie Lu: lul3\@illinois.edu

@@

| Item          | Description                                                                                                                                                                                    |
|---------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| Covariates    | aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances) |
| Specification | `asinh(aid) ~ asinh(coverage) + asinh(visits) + covariates + recipient + year`                                                                                                                 |
| Estimation    | OLS (CR1 errors), Tobit (random recipient intercepts), Logit/Selection (random recipient intercepts), Level/OLS (CR1 errors), Lagged IV (CR1 errors), Lewbel IV (CR1 errors).                  |

>>>>

-   Like Western donors, China should wield international aid, in part, to generate goodwill toward Beijing.
-   We know that this has been important for the US (e.g. tsunami relief to Indonesia in 2004)
-   There is some evidence that the perception fo Beijing's influence in developing countries is growing (per differences in 2014 and 2017 waves of AidData surveys of policymakers in 126 countries)

@@

-   Some argue that this is an intentional and strategic choice.

-   But it may have more to do with capacity (Dreher et al. 2018).

-   Limited transparency remains nonetheless.

@@

-   **Bilateral Diplomatic Visits** - AidData's *China's Public Diplomacy Dashboard*

-   **State-run Media Coverage** - Cline Center for Advanced Social Research's *Global News Index and Extracted Features Repository*

@@

-   **Bilateral Development Assistance** - AidData's *Global Chinese Development Finance Dataset*

@@

-   Diplomatic visits usually come with a policy agenda between two countries, and the two are expected to cooperate in various domains through their negotiations.

@@

**H1**: When developing countries receive more media exposure in *Xinhua*, they receive more foreign aid from China.

**H2**: When developing countries host more Chinese high-level diplomatic visits, they receive more foreign aid from China.

@@

| Variable               | Description                                                                                        | Source                                                                                               |
|------------------|---------------------------|----------------------------|
| Outcome                | bilateral ODA-like flows from China to developing countries                                        | AidData's *Chinese Development Finance Dataset*                                                      |
| Explanatory Variable 1 | the number of bilateral diplomatic visits hosted by recipients from Beijing                        | AidData's compiled yearly counts of bilateral official diplomatic visits from China                  |
| Explanatory Variable 2 | the number of times a developing country is mentioned in a year in the English edition of *Xinhua* | compiled from millions of *Xinhua* articles scraped by the Cline Center for Advanced Social Research |

@@

**Miles D. Williams**: milesdw2\@illinois.edu

**Lucie Lu**: lul3\@illinois.edu

@@

| Item          | Description                                                                                                                                                                                    |
|----------------|--------------------------------------------------------|
| Covariates    | aid recipient characteristics (GDP, presence of civil war, disasters, political and civil liberties) and bilateral characteristics between China and aid recipients (economic ties, alliances) |
| Specification | `asinh(aid) ~ asinh(coverage) + asinh(visits) + covariates + recipient + year`                                                                                                                 |
| Estimation    | OLS (CR1 errors), Tobit (random recipient intercepts), Logit/Selection (random recipient intercepts), Level/OLS (CR1 errors), Lagged IV (CR1 errors), Lewbel IV (CR1 errors).                  |
